Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-25 paper/paper.tex
edits to section 5

The Anglican language is a subset of Clojure\footnote{It would be
possible to support almost full Clojure by expanding all macros
in the Anglican source code. However, in Clojure, unlike in
Scheme~\cite{SDF+10} or Common Lisp~\cite{PC94}, the result
of macro-expansion of derived special forms is not well
specified and implementation specific.}.  Anglican queries
are defined within \texttt{defquery}. The value of the last
expression in the query body is the result of the query.
\begin{lstlisting}[style=default]
(defquery name doc-string? param? expr*)
\end{lstlisting}
Anglican functions outside of a query are defined using
\texttt{defm} with the same syntax as Clojure \texttt{defn},
however \texttt{name} is bound to an Anglican function.
\begin{lstlisting}[style=default]
(defm name doc-string? [param*] expr*)
\end{lstlisting}
Within the body of \texttt{defquery} and \texttt{defm}, the
following special forms are supported, with syntax and semantics 
matching those of Clojure:
\begin{lstlisting}[style=default]
(if test then else?)
(when test expr*)
(cond clause*)
(case expr clause* default?)
(let [binding*] expr*)
(and expr*)
(or expr*)
(fn name? [param*] expr*)
(loop [binding*] expr*)
(recur expr*)
\end{lstlisting}
In \texttt{defquery} parameter, \texttt{let} bindings, and
\texttt{fn} argument lists, Clojure vector destructuring is
supported. Literals for atomic types and compound literals for
vectors, hash maps, and sets are supported just like in Clojure.

Clojure provides special forms \texttt{loop} and \texttt{recur}
for writing tail-recursive programs.  Anglican programs are
CPS-converted and do not use the stack; recursive calls
in Anglican cannot lead to stack overflow.  However,
\texttt{loop}/\texttt{recur} is provided in Anglican for
convenience as a way to express loops. Unlike in Clojure though,
\texttt{recur} supported only inside a \texttt{loop}.

>>>>

The Anglican language is a subset of Clojure\footnote{It would be
possible to support almost full Clojure by expanding all macros
in the Anglican source code. However, in Clojure, unlike in
Scheme~\cite{SDF+10} or Common Lisp~\cite{PC94}, the result
of macro-expansion of derived special forms is not well
specified and implementation specific.}.  Anglican queries
are defined within \texttt{defquery}. The value of the last
expression in the query body is the result of the query.
\begin{lstlisting}[style=default]
(defquery name doc-string? param? expr*)
\end{lstlisting}
Anglican functions outside of a query are defined using
\texttt{defm} with the same syntax as Clojure \texttt{defn},
however \texttt{name} is bound to an Anglican function.
\begin{lstlisting}[style=default]
(defm name doc-string? [param*] expr*)
\end{lstlisting}
Within the body of \texttt{defquery} and \texttt{defm}, the
following special forms are supported, with syntax and semantics 
matching those of Clojure:
\begin{lstlisting}[style=default]
(if test then else?)
(when test expr*)
(cond clause*)
(case expr clause* default?)
(let [binding*] expr*)
(and expr*)
(or expr*)
(fn name? [param*] expr*)
(loop [binding*] expr*)
(recur expr*)
\end{lstlisting}
In \texttt{defquery} parameter lists, \texttt{let} bindings, and
\texttt{fn} argument lists, Clojure vector destructuring is
supported. Literals for atomic types and compound literals for
vectors, hash maps, and sets are supported just like in Clojure.

Clojure provides special forms \texttt{loop} and \texttt{recur}
for writing tail-recursive programs.  Anglican programs are
CPS-converted and do not use the stack; recursive calls
in Anglican cannot lead to stack overflow.  However,
\texttt{loop} and \texttt{recur} are provided in Anglican for
convenience as a way to express loops. Unlike in Clojure though,
\texttt{recur} is supported only inside a \texttt{loop}.
